Individual Partisan Harm and Utility in Redistricting

### 2021-10-14 paper/paper.Rmd
-basically

```{=tex}
\begin{restatable}{prop}{propcomp} \label{prop:comp}
Basically, if turnout is equal across districts, for an election $v\in\Elecs$ and districting plan $q\in\Plans$ and two political parties, we have
\begin{align*}
    \E[U^{(L)}\mid V=v, Q=q] &= \frac{1}{2|D|}\sum_{d\in D}
        \qty|\frac{\votes^{(p_a)}}{\votes^{(p_b)} + \votes^{(p_b)}}-\half| \\
    &= \half T_p(v,q) = \frac{\mathrm{comp}_\alpha(v,q)}{1+\alpha T_e(v_q)}.
\end{align*}

>>>>

```{=tex}
\begin{restatable}{prop}{propcomp} \label{prop:comp}
If turnout is equal across districts, for an election $v\in\Elecs$ and districting plan $q\in\Plans$ and two political parties, we have
\begin{align*}
    \E[U^{(L)}\mid V=v, Q=q] &= \frac{1}{2|D|}\sum_{d\in D}
        \qty|\frac{\votes^{(p_a)}}{\votes^{(p_b)} + \votes^{(p_b)}}-\half| \\
    &= \half T_p(v,q) = \frac{\mathrm{comp}_\alpha(v,q)}{1+\alpha T_e(v_q)}.
\end{align*}
